Architectures and Open pNets

### 2018-03-27 2018-Arch-pNets/arch-pNets.tex
alphas and betas
notations in weak + ref a forte

\todoLH{Guard syntax???}
\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\\noteSB{I would not put a new line here}
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} \\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\mprset{myfraction=\reddottedrule}\inferrule
    		{
    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}

	\begin{description}
		\item[{\bf Tr2:}]\noteSB{I do not understand why the second line $pNet_m \models\dots$ is not subsumed by the first one?}
	\end{description}

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |g \\
    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

>>>>

\todoLH{Guard syntax???}
\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes\footnote{Typing can 
be added to pNets by defining and checking their interfaces, called 
sort~\cite{HMZ-FORTE2016}}:
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} \\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\mprset{myfraction=\reddottedrule}\inferrule
    		{
    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}

%OLD	\begin{description}
%		\item[{\bf Tr2:}]\noteSB{I do not understand why the second line $pNet_m 
%\models\dots$ is not subsumed by the first one?}
%	\end{description}
%	
%	\noindent
%    $\inferrule
%    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
%    \alpha' |g \\
%    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
%    	\forall m\!\!\in\!\! I. 	
%    {\left(\begin{array}{l}
%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
%    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
%		{ \pNet_m 
%    	 \models
%    	\inferrule*[myfraction=\reddottedrule]
%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {v_m}
%    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
%\end{array}\right)}\\
%    	%\land
%    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
%     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
%    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
%    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
%    		I' = \biguplus_{m\in I}\!\! I_m'
%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
%    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
%    }
%    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
%    	\models
%    	{\inferrule*[myfraction=\reddottedrule]
%    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
%    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
%    		\Post_m}
%    		{\ostate{s_i^{i\in L}} \OTarrow {v}
%    			\ostate{(s_i^\prime)^{i\in L}}}
%    	}
%    }
%    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}
